\documentclass[a2paper, 10pt]{article}
\usepackage[a2paper]{geometry}
\usepackage[dvips]{color,graphicx}
\usepackage[dvips, bookmarks, colorlinks=false]{hyperref}
\usepackage{supertabular}
\usepackage{longtable}
\usepackage{tabularx}

%\pdfpagewidth and \pdfpageheight is only good for pdflatex
%\pdfpagewidth 13in
%\pdfpageheight 22in

\addtolength{\textheight}{10cm}
\addtolength{\textwidth}{5cm}
\addtolength{\hoffset}{-3cm}
\addtolength{\voffset}{-3cm}

%opening
\title{Report of the sequences of 2010 accessions in view of 149-snp data}
\author{Yu Huang}

\begin{document}

\maketitle

\begin{abstract}
\end{abstract}

\section{Group the 2010 accessions}

2010 data is from database at on papaya.usc.edu. 3 affiliated tables, accession, alignment and sequence.

The 149-snp data is from database stock on natural.uchicago.edu.

244 out of the 248 2010 accessions are matched to ecotypes in the stock database.

Based on the number of fragments, 248 2010 accessions are grouped into five tables. The number of 149 snps falling into these alignments is also shown. Table~\ref{tatg0} corresponds to 1 to 10 fragments. Table~\ref{tatg1} corresponds to 10 to 50 fragments. Table~\ref{tatg2} corresponds to 100 to 150 fragments. Table~\ref{tatg3} corresponds to 150 to 200 fragments. Table~\ref{tatg4} corresponds to 1300 to 1600 fragments.

The 2010 sequence fragments are too short in the genome scale. Instead of looking like blocks, they look like ticks crossing the chromosome.

alignment-type: a unique combination of genomic fragments. different combination has different alignment-type assigned.

\input{alignment_type_tables_figures.tex}

\end{document}
